**The status of the microbial census: an update**

### 2015-11-20 doc/notebook/Archaeal_data_acquisition.Rmd
Change metadat files to be *.v123.metadata
Metadata typos

#correct typos:
metadata$category[metadata$category == 'AQD'] <- 'AQO'
metadata$category[metadata$category == 'AQHS'] <- 'AQH'
metadata$category[metadata$category == 'AQS'] <- 'AQMS'
metadata$category[metadata$category == 'VD'] <- 'BD'
metadata$category[metadata$category == 'BM'] <- 'BI'
metadata$category[metadata$category == 'AH'] <- 'AQH'

#... and we output the metadata file...
write.table(metadata, file="data/mothur/archaea.final.metadata", sep="\t")

>>>>

#correct typos:
metadata$category[metadata$category == 'AQD'] <- 'AQO'
metadata$category[metadata$category == 'AQHS'] <- 'AQH'
metadata$category[metadata$category == 'AQS'] <- 'AQMS'
metadata$category[metadata$category == 'VD'] <- 'BD'
metadata$category[metadata$category == 'BM'] <- 'BI'
metadata$category[metadata$category == 'AH'] <- 'AQH'
metadata$category[metadata$category == 'BDBD'] <- 'BD'

#... and we output the metadata file...
write.table(metadata, file="data/process/archaea.v123.metadata", sep="\t")
